\documentclass[12pt]{article}
	\title{Math 480 Presentation 1: Outline}
	\author{Marcus Yamaguchi}
	\date{Febuarary 2017}
\begin{document}
	\maketitle
	This presentation is divided into three sections. I will introduce the topic of, "Why I chose Math as my major?" as the subject of my presentation. In this introduction I will briefly explain how my personal experience is related to the topic of section 1. The objective of this presentation will be to explain how I came to chose math based on the topics discussed in sections two and three, ("The reasons I love math", "How can math be used for good"). In conclusion, I will briefly discuss some of my more immediate individual goals as a potential math major. Below is an outline of my primary talking points.\par 
		
	\section{Why I choose Math as my major:}
		\subsection{Reason:I want to help people}
			\begin{itemize}
				\item Life is just better when you do
				\item I have had many good teachers/mentors
			\end{itemize}
		\subsection{Reason:I want to learn}
			\begin{itemize}
				\item Learning makes me feel alive
				\item Learning is the first step to teaching
			\end{itemize}
	\section{What do I love about mathematics:}

		\subsection{I like challenging problems: Math can be a puzzle/game}
			\begin{itemize}
				\item Math provides a means to solve challenging problems.
				\item Math provides a means to imagine new problems. 
			\end{itemize}
		\subsection{I like to have choices:Math branches into many fields}
			\begin{itemize}
				\item Math can be used to interpret other fields of knowledge
				\item Math can be used to develop new fields of knowledge
			\end{itemize}
		\subsection{I don't like making decisions: Math can model systems}
			\begin{itemize}
				\item Math can be used to structure or organize data="knowledge/experience"
				\item Math can be used to analyze complex systems
			\end{itemize}
	
	\section{How mathematics be used for good?}
	
		\subsection{Example: Math and Education}
			\begin{itemize}
				\item Math is a tool to develop critical thinking
				\item Math is a way to evaluate curriculum/teaching methods
			\end{itemize}
		
		\subsection{Example: Math in Government}
			\begin{itemize}
				\item Math is a way to provide feedback for government services
				\item Math is a way to provide strategic analysis for governments
			\end{itemize}
		\subsection{Example: Math in Technology/Science}	
			\begin{itemize}
				\item Math provides the tools to tech innovation
				\item Math is a platform to imagine and create
			\end{itemize}

\end{document}